---
title: "Seed Pod Wind Dispersal of Holmgren’s Milk-vetch, Astragalus holmgreniorum"
author: "Sydney Houghton"
date: "4/25/2018"
output:
  pdf_document: default
  html_document: default
---
Astragalus holmgreniorum is a federally listed endangered endemic perennial herb of the Northern Mojave Desert near St. George, UT. Conservation efforts are in motion to take collected seeds and disperse them into suitable habitat further from current threats. The morphological characteristics of the legume pods exhibit aerodynamic qualities after detaching from the mother plant. This study was performed to determine if wind dispersal is possible and if substrate, slope, or speed of wind have an affect. A runway was designed with different substrates: sand, small gravel, and medium gravel. Three degrees of slope were tested: no slope, upslope and downslope. Three speeds of wind (4.3 m/s, 7.1 m/s, 10.7 m/s) were provided by a fan to mimic habitat and environmental conditions in a controlled laboratory setting. For each treatment combination a new group of pods was tested totaling 324 individuals each trialed at two orientations to the wind. 

```{r}
setwd("/Users/sydneyhoughton/Desktop/Astragalus holmgreniorum /Wind Dispersal study/")
list.files()

dat = read.csv("Combined_data.csv")

dat$X = NULL
dat$distance..inches. = NULL
```

```{r}
aov1 = aov(distance..cm. ~ substrate, data = dat)
summary(aov1)
# reject NULL hypothesis, substrate matters!
aov2 = aov(distance..cm. ~ slope, data = dat)
summary(aov2)
# reject NULL hypothesis, slope matters!
aov3 = aov(distance..cm. ~ orientation, data = dat)
summary(aov3)
# accept NULL hypothesis, oreientation does not have a significant effect
aov4 = aov(distance..cm. ~ time.s., data = dat)
summary(aov4)
# reject NULL hypothesis, time has significance but not sure what this means. INVESTIGATE MORE
aov5 = aov(distance..cm. ~ initial_mass.g., data = dat)
summary(aov5)
# accept NULL hypothesis, oreientation does not have a significant effect

mod1 = aov(distance..cm. ~ substrate*slope*time.s., data = dat)
summary(mod1)
```


```{r echo=FALSE}
library(stargazer)
stargazer(attitude, type = 'text')

```